Initial Analysis

### 2019-08-20 Initial_Analysis.Rmd
Created file to deal with country duplications

       ## Run the lapply in parallel 
       return( parLapply( cl, ...) )
    }, finally = {        
       ## Stop the cluster
       stopCluster(cl)
    })
}

@@

## end mclapply.hack.R

@@

# Transboundary data
Spp <- list.files(Results_Path)
Results_Data <- GetTransResults(Spp)

Clean_Results <- Results_Data %>% 
  filter(is.na(Trans_Index)) %>% 
  select(1:5)

length(unique(Clean_Results$TaxonKey))

head(Clean_Results)
```

@@

This might be fixed with Tayler's data of EEZs to ISOs

@@

@@

```{Number_Tran_country, eval =T, echo =F}
# TI of 10% and MI > 50

TenFifty <- Clean_Results %>% 
  filter(Model_Index == 100,
         Area_Index >= 0.25,
         Area_Index <= 0.75
         ) %>% 
  group_by(Name=Country_Territory,Model_Index) %>% 
  summarise(
    n_trans = length(unique(TaxonKey)),
    n_countries = length(unique(Neighbor_Territory))
    ) 
  filter(Model_Index == 100)
  # head(Results_Data)

@@

World_EEZs_simple <- World_EEZs %>% 
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
  left_join(TenFifty, by ="Name") #%>%
  # filter(!is.na(n_trans)) #%>%
  # st_transform(crs = 3832)

@@

ggsave("R2_100_25_Fine_plot.png",
       plot = Plot,
       width = 16,
       height = 8,
       units = "in",
       path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
)

### Map exploration

# Salvador <- Results_Data %>% 
#   filter(Name == "El Salvador",
#          Model_Index >= 50)
# 
# Guat_Pac <- Results_Data %>% 
#   filter(Name == "Guatemala (Pacific)",
#          Model_Index >= 50)

  Area_Index_D <- Merged_data %>% 
    filter(Area_Index > 0.10,
           Area_Index < 0.90)

Spp_Results <- Results_Data %>% 
  filter(Model_Index >= 50#,
         # Trans_Index >= 0.10
         ) %>% 
  group_by(TaxonKey,Model_Index) %>% 
  summarise(n_Trans_Spp = n()/2)

ggplot(Spp_Results) +
  geom_bar(
    aes(
      x = as.character(TaxonKey),
      y = n_Trans_Spp
    ),
    stat = "identity"
  ) +
  facet_wrap(~Model_Index,
             scales = "free")

@@

```{r, Trans_Results, eval = F, echo = F}
```

>>>>

       ## Run the lapply in parallel 
       return( parLapply( cl, ...) )
    }, finally = {        
       ## Stop the cluster
       stopCluster(cl)
    })

@@

}
## end mclapply.hack.R

@@

# Transboundary data
Spp <- list.files(Results_Path)
Results_Data <- GetTransResults(Spp)
head(Results_Data)
unique(Results_Data$Model_Index)
length(unique(Results_Data$TaxonKey)) #672 spp

Clean_Results <- Results_Data

@@

This might be fixed with Tayler's data of EEZs to ISOs... He did it manually so it does not work!

@@

## Creating a subset dataset so i can work on my laptop and not remoteley
SubsetData <- TenTwenyfive %>% 
  filter(Name=="USA (East Coast)")

write.csv(SubsetData,
          "SubsetData.csv",
          row.names = F)
```

@@

```{Number_Tran_country, eval =F, echo =F}
# TI of 10% and MI > 50

TenTwenyfive <- Clean_Results %>% 
  filter(Model_Index == 100,
         Area_Index >= 0.25,
         Area_Index <= 0.75
         ) %>% 
  group_by(Name=Country_Territory,Model_Index) %>% 
  summarise(
    n_trans = length(unique(TaxonKey)),
    n_countries = length(unique(Neighbor_Territory)),
    Trans_Rate = n_trans/n_countries
    ) 
  filter(Model_Index == 100)
  # head(Results_Data)

@@

World_EEZs_simple <- World_EEZs %>%
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
  left_join(TenTwenyfive, by ="Name") #%>%
  # filter(!is.na(n_trans)) #%>%
  # st_transform(crs = 3832)

@@

ggsave("R4_100_25.png",
       plot = Plot,
       width = 16,
       height = 8,
       units = "in",
       path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
)

@@
